\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

%----------FONT OPTIONS----------
% Sans-serif: \usepackage[sfdefault]{roboto}
% Serif: \usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
{\Huge \scshape \href{https://sharmavaibhav31.github.io/sharmavaibhav31/}{Vaibhav Sharma}} \\ \vspace{1pt}    Bangalore, India \\ \vspace{1pt}
    \small \faPhone\ +91 70107 63467 ~ 
    \href{mailto:sharma31stmay@gmail.com}{\faEnvelope\ \underline{sharma31stmay@gmail.com}} ~ 
    \href{https://linkedin.com/in/sharmavaibhav31}{\faLinkedin\ \underline{linkedin.com/in/sharmavaibhav31}} ~
    \href{https://github.com/sharmavaibhav31}{\faGithub\ \underline{github.com/sharmavaibhav31}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Mangalore Institute of Technology and Engineering}{Sep 2023 -- Jun 2027}
{B.E. Computer Science and Engineering (CGPA: 9.43)}{Karnataka, India}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages:} Java, C, Python, SQL \\
\textbf{Backend:} Spring Boot, REST APIs, Flask \\
\textbf{Databases:} PostgreSQL, MySQL, Firestore \\
\textbf{Systems:} Linux, Seccomp, Namespaces, Process Isolation \\
\textbf{Tools:} Git, GitHub, Docker, Firebase, GCP
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{AI/ML Intern}{Sep 2025 -- Nov 2025}
{Infosys Springboard}{Virtual}
\resumeItemListStart
\resumeItem{Built backend APIs coordinating multiple ML inference models using Flask within an AI music generation system.}
\resumeItem{Implemented model preloading and fallback logic, reducing initialization latency by \textbf{45\%} and ensuring seamless inference workflows for high-concurrency requests.}
\resumeItem{Designed REST endpoints for music generation, metadata storage, and genre classification backed by MongoDB.}
\resumeItemListEnd

\resumeSubheading
{Flutter Developer Intern}{Jul 2025 -- Sep 2025}
{ClubChat Startup}{Remote}
\resumeItemListStart
\resumeItem{Contributed to a production mobile application serving \textbf{8,000+ users}.}
\resumeItem{Developed event feed and real-time chat features using Flutter and Dart.}
\resumeItem{Resolved \textbf{18+ stability issues} across two production releases through debugging and root-cause analysis.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Academic Timetable Scheduling System} $|$ Spring Boot, PostgreSQL, Docker}{2026}
\resumeItemListStart
\resumeItem{Built a backend scheduling system generating academic timetables across \textbf{8 semesters}.}
\resumeItem{Implemented constraint-based allocation preventing room, faculty, and section conflicts.}
\resumeItem{Designed \textbf{14 normalized JPA entities} with Flyway schema migrations and transactional rollback safety.}
\resumeItem{Containerized backend using Docker with role-based access control via Spring Security.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Offline AI Assistant Shell} $|$ C, Linux Syscalls, Seccomp}{2025}
\resumeItemListStart
\resumeItem{Built a secure C-based shell integrating an offline LLM using \texttt{llama.cpp}.}
\resumeItem{Implemented sandboxing using \textbf{Seccomp syscall filtering}, Linux namespaces, and resource limits.}
\resumeItem{Added syscall auditing and integrity checks to validate secure execution under constrained environments.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{URL Shortener System} $|$ Spring Boot, React}{2026}
\resumeItemListStart
\resumeItem{Developed a full-stack URL shortening service implementing Base62 encoding and click tracking.}
\resumeItem{Implemented thread-safe sliding-window rate limiting using ConcurrentHashMap.}
\resumeItem{Designed REST APIs for URL creation, redirection, and analytics dashboards.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership \& Community}
\resumeSubHeadingListStart

\resumeSubheading
{President, Coders Club}{Oct 2025 -- Present}
{MITE Campus}{}
\resumeItemListStart
\resumeItem{Organized \textbf{Hack n' Seek}, a hybrid technical event with \textbf{700+ online participants} and \textbf{180+ on-site attendees}.}
\resumeItem{Mentor students in Git, Data Structures, and backend development.}
\resumeItemListEnd

\resumeSubheading
{Open Source Contributor}{Feb, 2026}
{Aperture Project}{}
\resumeItemListStart
\resumeItem{Contributed to the GitCanvas open-source codebase with \textbf{2 pull requests merged} after maintainer review.}
\resumeItem{Opened and discussed issues, helping identify bugs and suggesting fixes to other contributors.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}